---
title: "p8105_hw5_fx2184"
author: "Fei"
date: "2022-11-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readr)
library(rvest)
library(purrr)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 2
```{r, meassage = FALSE}
# read the data from the web 
url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicides_raw = read_csv(url)
```
* The raw dataset include `r nrow(homicides_raw)`observations of homicides reported criminal homicides over the past decade in 50 of the largest American cities, and `r ncol(homicides_raw)` key variables, they are `r homicides_raw %>% names`. 
* some reported `unknown` under variable victim age, sex and race. 
* the `lat` contains `r sum(is.na(homicides_raw$lat))` missing value, and `lon` contains `r sum(is.na(homicides_raw$lon))` missing value, 
* the raw data contains 3 numeric variables: reported data. longitude and latitude, rest of the variables are designed as character variables. 
* The data contains only one observation from `Tulsa` with state `OK`, which does not make sense. So I assume it's a typo, I will delete this row in the further cleaning step. 

## clean the raw data and create city_state and resolved
```{r}
homicides = homicides_raw %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state,sep = ", "),
         resolved = case_when(
           disposition == "Closed by arrest" ~ "solved",
           disposition ==  "Open/No arrest" ~ "unsolved",
           disposition ==  "Closed without arrest" ~ "unsolved"
         )) %>% 
  filter(city_state != "Tulsa, AL") %>% 
  relocate(uid, city_state)
```

```{r}
#summarize within cities to obtain the total number of homicides and the number of unsolved homicides
total_homicides = homicides %>% 
  group_by(city_state) %>% 
  summarize(total_homicide = n(), unsolved = sum(resolved == "unsolved")) 

total_homicides %>% knitr::kable(align='c',col.names = c("City/State","Total Number of Homicids","Number of Unsolved "))
```


```{r}
# For the city of Baltimore, MD,estimate the proportion of homicides that are unsolved
prop_baltimore =  prop.test(total_homicides %>% filter(city_state == "Baltimore, MD") %>% pull(unsolved),
                            total_homicides %>% filter(city_state == "Baltimore, MD") %>% pull(total_homicide))
broom::tidy(prop_baltimore)[,c(1,5,6)] 

```

The estimate proportion of unsolved homicides in Baltimore, MD is `r prop_baltimore$estimate` with confidence interval 
```{r}
# Estimate proportion of homicides that are unsolved for each of the cities 
# extract both the proportion of unsolved homicides and the confidence interval for each.
prop_cities = 
  total_homicides %>% 
  mutate(prop_test = purrr::map2(.x = unsolved, .y = total_homicide, ~prop.test(x = .x, n = .y)),
         tidy_test = purrr::map(.x = prop_test, ~broom::tidy(.x))) %>% 
  unnest(tidy_test) %>% 
  select(city_state, estimate, conf.low, conf.high)

prop_cities%>% knitr::kable(align='c',col.names = c("City/State","Estimate","Confidence(lower)","Confidence(upper)"))
```

## create a plot showing the estimates and CI

```{r}
prop_cities%>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(x = "City",
       y = "Estimate",
       title = "Estimates and Confidence Intervals of Porportion of Unsolved Homicides for Each City") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
# Problem 3: Explore power in a one-sample t-test.

```{r,warning=FALSE,message=FALSE}
set.seed(1)
```
## generate the function 
```{r}
ttest = function(n = 30, mu, sigma = 5) {

  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  test_data =  t.test(sim_data, mu = 0, conf.level = 0.95) 
  
  sim_data %>% 
    summarize(
      mu_hat = pull(broom::tidy(test_data), estimate),
      p_value = pull(broom::tidy(test_data), p.value)
    )
}
```

## generate 5000 datasets from the model $X \sim Normal[\mu, \sigma]$ 

```{r}
set.seed(1)

sim_result = tibble(mu = c(0:6)) %>% 
              mutate(
                output_list = map(.x = mu, ~rerun(5000,ttest(mu=.x))),
                estimate_df = map(output_list, bind_rows)
              ) %>% 
    select(-output_list) %>% 
    unnest(estimate_df)
```



```{r}
#showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ
#on the x axis. Describe the association between effect size and power.
sim_result %>% 
  group_by(mu) %>% 
  summarize(rej_num = sum(p_value <0.05),
            total = n(),
            rej_prop = rej_num/total) %>% 
  ggplot(aes(x=mu, y = rej_prop))+
  geom_point(alpha = 0.5)+
  geom_line()+
  geom_text(aes(label = round(rej_prop,3)), vjust = -1, size = 3)+
  labs(
    title = "Association Between Effect Size and Power",
    x = "True Mean", y = "Power of Test"
  )+
  scale_x_continuous(n.breaks = 6)+
  scale_y_continuous(n.breaks = 10)

```

```{r}
#Make a plot showing the average estimate of μ̂， on the y axis and the true value of μ，  on the x axis. 
sim_result %>% 
  group_by(mu)%>% 
  summarize(average_mu = mean(mu_hat)) %>% 
  ggplot(aes(x = mu, y=average_mu))+
  geom_point()+
  geom_line()+
  geom_text(aes(label = round(average_mu,3)),vjust = -1, size = 2)+
  scale_x_continuous(breaks = 1:6)+ 
  scale_y_continuous(breaks = 1:6)+
  labs(
    title = "Association Between True Mean and Average Estimate of Mean",
    x = "True Mean",
    y = "Average Estimate of Mean"
  )
```
```{r}
#Make a second plot showing the average estimate of μ_hat only in samples for which the null was rejected on the y axis and the true value of μ on the x axis
sim_reject = sim_result %>% 
  group_by(mu)%>% 
  filter(p_value<0.05) %>%
  summarize(average_mu = mean(mu_hat))

sim_result%>% 
  group_by(mu)%>%
  summarize(average_mu = mean(mu_hat)) %>% 
  ggplot(aes(x=mu, y= average_mu, color = "Total sample"))+
  geom_point()+
  geom_line()+
  geom_text(aes(label = round(average_mu,3)),vjust = -1)+
  geom_point(data = sim_reject, aes(x= mu, y = average_mu, color = "Rejected samples"))+
  geom_line(data = sim_reject, aes(x= mu, y= average_mu, color = "Rejected samples"))+
  geom_text(data = sim_reject, aes(label = round(average_mu, 3), color = "Rejected samples"), vjust = -1)+
  scale_x_continuous(breaks = 1:6) +
  scale_y_continuous(breaks = 1:6) +
  labs(
    title = "Association between ture mean and average estimates",
    x= "True Mean",
    y= "Average estimate of mean (reject null samples)"
  )
```


