---
title: "p8105_hw5_fx2184"
author: "Fei"
date: "2022-11-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readr)
library(rvest)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# problem 2
```{r, meassage = FALSE}
# read the data from the web 
url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicides_raw = read_csv(url)
```
* The raw dataset include `r nrow(homicides_raw)`observations of homicides reported criminal homicides over the past decade in 50 of the largest American cities, and `r ncol(homicides_raw)` key variables, they are `r homicides_raw %>% names`. 
* some reported `unknown` under variable victim age, sex and race. 
* the `lat` contains `r sum(is.na(homicides_raw$lat))` missing value, and `lon` contains `r sum(is.na(homicides_raw$lon))` missing value, 
* the raw data contains 3 numeric variables: reported data. longitude and latitude, rest of the variables are designed as character variables. 


```{r}
#clean the raw data and create city_state varialbe 
homicides = homicides_raw %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state,sep = ", "),
         resolved = case_when(
           disposition == "Closed by arrest" ~ "solved",
           disposition ==  "Open/No arrest" ~ "unsolved",
           disposition ==  "Closed without arrest" ~ "unsolved"
         )) %>% 
  filter(city_state != "Tulsa, AL") %>% 
  relocate(uid, city_state)
  
```




